\begin{abstract}
\addcontentsline{toc}{section}{Abstract}
% +++++++++++++++++++++++++

This master's thesis aims at training a deep neural network for the selection of "good" objects which collectively represent a very large dataset. It is essential to choose some objects as the representative members of the dataset which can act as a source library. This source library is then utilized to evaluate the performance of the transfer learning approaches in bin picking applications. The goal of this thesis is to train a deep neural network that is complex enough to accurately learn the necessary features of an object to be able to classify them later on into cluster and evaluate different clustering algorithm for this purpose. During the course of the thesis, the challenges and motivation of this work is discussed. Existing work in the literature has been reviewed thereafter. The fundamental concepts that are essential for the development of this whole pipeline of training a neural network to get the latent space representations of the objects in the dataset and then clustering them have been discussed next. Then comes an elaborate documentation of the neural network used for this purpose and the different clustering algorithms prevalent in the domain. Subsequently, the idea of a new clustering algorithm has been proposed keeping in mind the constraints and limitations in this particular use-case. The performance of the different clustering algorithms has been evaluated in detail. An extension study on fine-tuning the model hyperparameters has been performed to improve the performance of the deep neural network and the clustering algorithms. The existing deep neural network at \ac{IPA} has been used as a baseline to compare the performance of the proposed method. Finally, a critical analysis of the results has been performed keeping in mind the goals, limitations and the scope for further development. 

\vspace{20mm}

\textbf{Keywords}: Feature representations, deep neural network, autoencoder, clustering algorithms, bin picking
% +++++++++++++++++++++++++
\end{abstract}